Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-06 manuscript.Rmd
show citation in markdown example closes #210
dont use svg version

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (`Git`), dependency tracking (`Make`), software management (`Docker`), and dynamic document generation (`R Markdown`). `Git` tracks changes to the project over time. `Make` manages dependencies among the files. `Docker` provides a container in which the final report is built using dynamic document generation in `R Markdown`. Reproduced from @Peikert2019 licensed under [CC BY 4.0](https://creativecommons.org/licenses/by/4.0).  "}
# file gets downloaded in Makefile
knitr::include_graphics(here::here("images/nutshell.svg"), auto_pdf = TRUE)
```

@@

`R Markdown` is a type of dynamic document well-suited to the RStudio user interface.
The text of an `R Markdown` is formatted by `Markdown` (see @xieMarkdownDefinitiveGuide2019 for technical details and @xieMarkdownCookbook2020 for practical guidance).
The code mostly consists of R-code (although other programming languages are supported, like Python, C++, Fortran, etc).
The following example serves to illustrate the `Markdown` syntax. 
It shows how to create a heading, a word in bold font, and a list of several items in `Markdown`:

@@

Normal text.
Important **word** in bold.

>>>>

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (`Git`), dependency tracking (`Make`), software management (`Docker`), and dynamic document generation (`R Markdown`). `Git` tracks changes to the project over time. `Make` manages dependencies among the files. `Docker` provides a container in which the final report is built using dynamic document generation in `R Markdown`. Reproduced from @Peikert2019 licensed under [CC BY 4.0](https://creativecommons.org/licenses/by/4.0).  "}
# file gets downloaded in Makefile
knitr::include_graphics(here::here("images/nutshell.pdf"))
```

@@

`R Markdown` is a type of dynamic document well-suited to the RStudio user interface.
The text of an `R Markdown` is formatted by `Markdown` (see @xieMarkdownDefinitiveGuide2019 for technical details and @xieMarkdownCookbook2020 for practical guidance).
The code mostly consists of R-code (although other programming languages are supported, like Python, C++, Fortran, etc).
The following example serves to illustrate the `Markdown` syntax. 
It shows how to create a heading, a word in bold font, a citation and a list of several items in `Markdown`:

@@

Normal text.
Important **word** in bold.
A citation: @einstein1935 did important research on this topic.
